---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# Adaptive Hellinger Distance (AHD) for Testing Independence between two random vectors
<!-- badges: start -->
[![R-CMD-check](https://github.com/wzhong41/semidist/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/wzhong41/semidist/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
The goal of package `AHD` is to provide an easy way to implement the Adaptive Hellinger Distance(AHD). 

Key features:

- A rank-based independence test using the AHD.

- The AHD-based tests address the potential zeros in the denominators of the HHG test statistic.

- The AHD-based tests inherit the robustness of the HHG test while conservatively improving its performance.

- The AHD tests can be regarded as a crucial extension of the HHG test.


## Installation
To install `AHD`, 
``` r
devtools::install_github("JiujingWu/AHDPackage")
```


## Example
Here is a simple example showing how to use `AHD` to compute the test statistic between two random vectors, 
and apply the test statistic on testing the independence and conduct p-values combination. 

```{r example}
library(AHD)

n <- 50
x <- runif(n, 0, 1)
y <- x * (sample(c(-1, 1), size = n, replace = TRUE)) + runif(n, -0.5, 0.5)

AHD <- AHD(x, y)
AHD_4bins_pval <- AHD_test_4bins(x, y, B = 199)
p_AHD <- AHD_4bins_pval$pvalue
p_AHD_11 <- AHD_4bins_pval$pvalue11
p_AHD_12 <- AHD_4bins_pval$pvalue12
p_AHD_21 <- AHD_4bins_pval$pvalue21
p_AHD_22 <- AHD_4bins_pval$pvalue22

p_val_com <- P_VALUE_COMB(p_AHD_11, p_AHD_12, p_AHD_21, p_AHD_22)
```

